CompDec - Detect the Compression Algorithm of File Fragments using Convolutional Neural Networks

### 2020-12-31 paper/model.tex
Adjust network visualization to accurately show 1D classifier

\pic[shift={(1,0,0)}] at (pool4-east) 
    {Box={
        name=conv6,
        caption= ,
        xlabel={{, }},
        zlabel=2048,
        fill=\ConvColor,
        height=32.67000000000001,
        width=1,
        depth=32.67000000000001
        }
    };

\pic[shift={(1,0,0)}] at (conv6-east) 
    {Box={
        name=conv7,
        caption= ,
        xlabel={{, }},
        zlabel=2048,
        fill=\ConvColor,
        height=32.67000000000001,
        width=1,
        depth=32.67000000000001
        }
    };

>>>>

\pic[shift={(1,0,0)}] at (pool4-east) 
    {Box={
        name=conv6,
        caption= ,
        xlabel={{, }},
        zlabel=2048,
        fill=\ConvColor,
        height=2,
        width=1,
        depth=32.67000000000001
        }
    };

\pic[shift={(1,0,0)}] at (conv6-east) 
    {Box={
        name=conv7,
        caption= ,
        xlabel={{, }},
        zlabel=2048,
        fill=\ConvColor,
        height=2,
        width=1,
        depth=32.67000000000001
        }
    };
